The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-20 src/ms.tex
Small grammar correction

  One manifestation of this development realizing some features do not actually
  belong in the core package, either because they are of more general use
  outside of \astropypkg, or because they are too specialized. An example of the
  former is the copy of the IAU Standards Of Fundamental Astronomy (SOFA)
  software Collection\footnote{\url{http://www.iausofa.org}} \citep{sofa} that
  \astropy carried, as well as the \python wrappers for it.  Since this is more
  basic infrastructure, with a release cycle set by SOFA, it made more sense to
  create separate packages that \astropypkg can depend on: \package{ERFA}
  \citep{erfa} and \package{PyERFA} \citep{pyerfa}. An example of something that
  was too specialized was a Virtual Observatory sub-package (now removed).  Of
  its content, the Simple Application Message Protocol made sense to keep
  (\astropysubpkg{samp}), but other parts belonged more properly in {\tt
  Astroquery} (see Sect.~\ref{sec:astroquery}).

>>>>

One manifestation of this was the realization that some features do not actually
belong in the core package, either because they are of more general use
outside of \astropypkg, or because they are too specialized. An example of the
former is the copy of the IAU Standards Of Fundamental Astronomy (SOFA)
software Collection\footnote{\url{http://www.iausofa.org}} \citep{sofa} that
\astropy carried, as well as the \python wrappers for it.  Since this is more
basic infrastructure, with a release cycle set by SOFA, it made more sense to
create separate packages that \astropypkg can depend on: \package{ERFA}
\citep{erfa} and \package{PyERFA} \citep{pyerfa}. An example of something that
was too specialized was a Virtual Observatory sub-package (now removed).  Of
its content, the Simple Application Message Protocol made sense to keep
(\astropysubpkg{samp}), but other parts belonged more properly in {\tt
Astroquery} (see Sect.~\ref{sec:astroquery}).
